Global adjoint tomography -- Model GLAD-M25

### 2018-12-04 main.tex
update figures
Updates from ShareLaTeX

@@

To accomplish the transformation,
we first need to transform our 3D mesh --- which includes ellipticity, topography \& bathymetry, and undulations on internal boundaries --- into a spherical volume.
After these adjustments, we obtain a spectral element mesh for a perfect sphere,
that is, the sort of mesh we use for spherically symmetric earth models, such as PREM~\citep{PREM}.

>>>>

\section{Spherically symmetric average model}

In this appendix we determine the spherically symmetric (radial) average of model GLAD-M25.
To accomplish this,
we first need to transform the 3D spectral-element mesh --- which includes ellipticity, topography \& bathymetry, and undulations on internal boundaries --- into a spherical volume.
After these adjustments, we obtain a spectral-element mesh for a perfect cubed sphere~\citep{KoTr02a}.

In the spherical mesh, the model may be expressed in the form
\begin{equation}
    m(\mathbf{x})=\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}m^{\alpha\beta\gamma}\,h_{\alpha}(\xi)\,h_{\beta}(\eta)\,h_{\gamma}(\zeta)\,
    \quad ,
\end{equation}
where~$h_\alpha$ denotes a Lagrange polynomial, and where we have used the invertible mapping
\begin{equation}
    \mathbf{x}=\mathbf{x}(\xi,\eta,\zeta)
\end{equation}
between spatial points~$\mathbf{x}=\{x,y,z\}$ and Gauss-Lobatto-Legendre (GLL) points in the reference element~$\{\xi,\eta,\zeta\}$~\citep{KoTr99}.

The spherically symmetric part of the model is defined as
\begin{equation}
    \overline{m}(r)=\frac{1}{4\pi}\,\int_\Omega m(\mathbf{x})\,\mathrm{d} \Omega
    \quad,
\end{equation}
where~$r$ denotes the radius and~$\Omega$ the unit sphere.

Using 2D GLL quadrature~\citep{KoTr99} in the unit sphere,
the radial average may be determined numerically via GLL quadrature:
\begin{equation}
    \overline{m}(r)=\frac{1}{4\pi\,r^2}\,\sum_{\alpha,\beta}\omega_\alpha\omega_\beta\,m^{\alpha\beta}(r)\,J^{\alpha\beta}(r)
    \quad.
    \label{eq:radial_average}
\end{equation}
Here~$\alpha$ and~$\beta$ denote GLL points in the sphere with radius~$r$\,,
$\omega_\alpha$ denotes a GLL quadrature weight, and $J^{\alpha\beta}(r)$ is the 2D Jacobian of the mapping to the sphere.
It is important to carry out the summations in~(\ref{eq:radial_average}) at the elemental level to ensure that first-order discontinuities are honored in the process.

Figure~\ref{fig:global-average} shows the resulting radial averages of the isotropic shear and compressional wavespeeds for model~GLAD-M25
compared to 1D starting model~STW105~\citep{kustowski2008anisotropic} and PREM~\citep{PREM}.
The radial average of~GLAD-M25 remains very close to the radial starting model~STW105.
The main difference between these two models and~PREM
is the absence of the 220~km discontinuity and a lower~$V_p/V_s$ ratio in the top 200~km.
\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/1d_profile.pdf}
  \caption{1D radial shear and compressional wavespeed profiles for GLAD-M25, STW105, and PREM.
  The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}
  \label{fig:global-average}
\end{figure}

@@

To accomplish the transformation,
we first need to transform the 3D mesh --- which includes ellipticity, topography \& bathymetry, and undulations on internal boundaries --- into a spherical volume.
After these adjustments, we obtain a spectral element mesh for a perfect sphere,
that is, the sort of mesh used for spherically symmetric earth models, such as PREM~\citep{PREM}.
